Extended Early Adulthood and Attitude Change

### 2024-07-03 manuscript/formative_period_kk.Rmd
drafting

While we have focused on changes in the timing and structure of life course stages over the past 70 years as our primary focus, the past 70 years have also seen significant shifts in the broader social structure and cultural environment that might affect attitude stability independent of changes in life course structure. We briefly consider three broader changes here.

First, the number of people pursuing and completing higher education increased significantly over the window studied here [@schofer2005; @hout2012]. Existing work suggests that people with higher levels of education are more likely to express the same opinion over time in survey contexts [@alwin1991a; @alwin2007]. A population with higher levels of education, on average, might be more likely to hold stable opinions regardless of transformations in life course stages.

Second, technological changes have dramatically lowered barriers to accessing information, including information about social and political affairs that might facilitate stable opinion holding. Broadcast and cable television, followed by the internet and social media, have provided new channels for elites to communicate messages to the public and for people to acquire informaiton that makes opinion-holding easier.

Third, the past 70 years have seen extensive elite polarization around political and social affairs, as well broader public partisan alignment [@fiorina2008; @baldassarri2008]. People now receive clearer signals from cultural elites, including politicians, the news media, and others, about which beliefs and identities "go together" in the population, resulting in what DellaPosta (2020) calls an "oil spill" of polarization [@dellaposta2020]. This issue and identity alignment might make it easier for the public to identify what beliefs people like them "should" hold and hold them consistently [@zaller1992]. Geographic and social sorting into lifestyle "enclaves" also reinforce these processes, continually providing clearer signals about which opinions people should hold [@dellaposta2015].

@@

For reasons explained below, we identified questions that were asked in at least three different panels with at least one of those panels asking some respondents to answer the question at three or more separate time points. Because three of the GSS panels overlap considerably (2006-10, 2008-12, and 2010-14) and contain the same set of questions, we did not treat these as separate panels for the purposes of generating three distinct time points. In other words, questions needed to appear in these panels and an ANES panel to be included in our analysis. When question wording changed across panels, we harmonized response options to the question structure with the fewest response options.

@@

Table A1 in Appendix A outlines the questions included in our analysis, including their full question wording and response scale. For a small number of items where question wording remains consistent across panels but response scales differ, we harmonize by converting more fine-grained response scales to the more general scales, following the ANES time series.

@@

We are also interested in the effect of having undergone a set of life-course transitions on attitude stability to more directly test whether divergences in life course structure drove changes in attitude stability. To this end, we include a set of indicator variables capturing whether people have undergone certain demographic transitions. These include 1) whether a respondent is currently enrolled in school; 2) whether a respondent has ever been married; and 3) whether a respondent has ever had a child. We also include an indicator for whether a respondent reported completing college to separately explore whether higher rates of college completion explain changes over time across age groups.

@@

In this framework, the first-level equation models the absolute difference in a pair of responses to the same question given by the same respondent, similar to what was presented above. These equations are nested at the level of the survey item. In practice, the model presented in Eq \### is likely too complicated in the face of the data limitations we face. As part of our analysis, we compare the fully elaborated model to more Criterion models using model-selection criteria, specifically the Bayesian Information Criterion. For example, it could be the case that little predictive information is gained by allowing questions to have separate slopes for the relationship between age categories and duration over time.

@@

To distinguish between the influence of life course structure and other factors that might be affecting attitude stability, such as broader social forces, we calculate the expected rate of attitude change in later panels holding constant the proportion of respondents in each group who made certain demographic transitions.

## Weights

We focus on using weights that accounts for sampling design.

For the 2016-20 ANES panel, almost all questions are asked in either the pre- or post-election version of both surveys. The panel includes weights for . The single item that was asked in the pre- and post-election waves of the 2016 panel (polviews) is weighted using the pre- election weights.

For the 2020-22 ANES panel.

@@

The intercept term in Model 1 suggests that, on average, survey respondents in the 18-25 age group are expected to vary by almost a fifth of the response scale on average (18 points) in the most recent years of the survey, controlling for duration between observations, on any particular question. This is a rather high level of variance, but it is consistent with previous studies that find that on any particular question survey respondents tend to make large wave-to-wave changes, or that survey questions about political attitudes have high levels of measurement error [@ansolabehere2009; @converse1965]. At the same time, random-effect variance around this main intercept term is quite large ($\sigma_{\beta_0} = 5.9220$). On several questions, respondents are expected to change their responses by about 40 percent of the scale between observations, while on others almost no wave-to-wave change is expected, meaning people tend to respond with the same answer over time with low levels of measurement error or random change.

Duration between observations is positively associated with wave-to-wave absolute change. For every additional year between responses, the expected absolute change for respondents increases 1.1 points. As suggested above, there is no evidence to suggest that respondents in different age groups vary systematically in this kind of change. Random effect variance around this main effect is relatively small (s.d. = 0.36), meaning each one-year duration only increases the amount changed by between .5 and 1.5. Given the comparatively high level of wave-to-wave change independent of duration (18 points), our results broadly suggest that most wave-to-wave change is non-persisting, consistent with findings from other recent work [@kiley2020; @lersch2023].

The coefficients for age groups other than the reference category suggest that, on average, other age groups are more stable than people in the 18-25 age range in the most recent panels. Respondents in the 26-33 age group are about 1.1 points more stable on average, respondents in the 34-65 age group are about 2.2 points more stable on average, and respondents in the 65 and over age group are about 3.5 points more stable on average, than respondents in the 18 to 25 age group. This provides broad evidence for the "impressionable years" and "increasing persistence" hypotheses, as the youngest age groups are less stable than others, followed by the 26-33 age group.

People over 25 make slightly less change than people 18-25 for each additional year of observation, suggesting that the youngest age groups might be making more durable changes of opinion than their older counterparts, but these differences are small and substantively negligible, especially compared to the amount of non-persisting change.

Coefficients in Model 1 allow us to test several of the hypotheses outlined above. The intensification of early adulthood hypothesis (H3) generally suggests that the youngest respondents should make more change over time in more recent cohorts than their counterparts from earlier cohorts did when they were the same ages. The effect of year of observation in decades for people in the 18-25 age group ($\beta = 0.14345$, $t = 0.754$) is substantively small and not statistically significantly different from 0. On average, recent cohorts in this age group make approximately the same amount of wave-to-wave change in recent years as earlier cohorts did, accounting for the kinds of questions they were asked and time between responses. However, question-level random effects vary considerably around this main effect, with a standard deviation of about 1.43. This suggests that the overall flat trend obscures quite large question-level differences, with some questions becoming more stable and others becoming less stable. We return to consider these question-specific trends later.

Next, the extended early adulthood framework (H1) suggests that we should see a closing of the gap between people in the 18-25 and 26-33 age groups over time. The interaction between year of observation and the 26-33 age category is small and not statistically significant ($\beta = -0.03560$, $p=-0.361$), suggesting that people in this age group have not become any more or less likely to make changes of opinion since the earliest panels, have not become any more or less similar to the youngest respondents.

However, it is important to understand the full picture of change over time before drawing substantive conclusions. Table XXX shows that, in contrast to people in the 18-25 and 26-33 age range, respondents in older age groups (34-64 and 65+) do show a notable time trend -- people in these age ranges become more stable opinion holders over time. To more clearly illustrate overall trends, Figure XXX plots the predicted time level of change for respondents in each age category over time.

@@

To evaluate the specific effect of life-course changes, we attempt to control for these transitions. We re-estimate Model \### above, this time incorporating a series of indicator variables for whether people were students, had children, and were married. We also include an indicator variable for whether the respondent completed college to capture the effect of ... .

@@

@@

Theoretical models that explain the heightened malleability of attitudes during early adulthood by referencing the unique social conditions of that life phase suggest that significant changes in the timing of life course events should produce heightened rates of attitude change during early adulthood (18-25) or should extend rates of attitude updating later into life (ages 26-33). Given that Americans, on average, pushed back marriage, childbirth, and entering the workforce over the course of the 20th Century, we expected these social shifts to have some effect on the sources of attitude change, such as meeting new significant others, getting exposed to new kinds of information, or delaying social positions that expect stability. We tested that hypothesis by looking at the stability of political and social attitudes among different cohorts as they moved through the same age groups.

The results presented above suggest a more complicated picture than expected. Consistent with expectations, the youngest adults look similar to older adults in the earliest panels. While members of the youngest age categories (18-25 and 26-33) diverged from older members of the population in the rate at which they changed their opinions, showing more change than older respondents in the most recent panels, this shift was principally driven by an increase in stability among people in middle age and over 65, rather than increased opinion change among the youngest adults. We suggested that this aggregate divergence was driven by counter-vailing trends. First, consistent with our expectations, delays in life course transitions appear to push the youngest members of the population to make more attitude change over time. At the same time, a broad set of social forces worked to stabilize opinions for all members of the population, leading to divergence between the youngest adults and the rest of the population.

The broad pattern of results suggests a broad role for social structures to influence patterns of stable opinion holding. At the aggregate level, broad social currents such as increased levels of education, changes in media environments and access to information, and changes in aggregate social sorting appear to affect ...

At another level, social forces that structure the life course appear to produce different rates of change for people in different life stages.

Similarly, as life course transitions have been pushed back since the middle of the 20th Century, we expected to see decreased reliability and stability extend into the next age group (ages 26-33). However we see no clear evidence of changes in either stability or reliability. Attitude behavior of people in this group is consistently closer to that of people in the next oldest group (34 to 41) than to people the 18 to 25 age group. While social life for people in this group increasingly resembles the younger group, their attitude behavior tends to resemble older groups.

It does not appear that the lack of change is attributable to changes in questions over time. We observe the same patterns in stability and reliability of attitudes whether we focus only on questions that are replicated across panels .

@@

|                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                 |
|------------------------------------------------------------------------|
| There are theoretically relevant trade-offs from focusing only on the same questions over time. By focusing only on the same questions over time, we control for question content and structure and ensure that the trend over time is due to something other than changes in survey administration. Because our panels span more than five decades that saw dramatic improvements in survey question design, questions included in more recent surveys might simply be of higher quality, with less wave-to-wave change, than items included in older surveys.                                 |
| We face several limitations in trying to make broader claims. First, many of our age-group estimates of stability and reliability are based on relatively small samples and as a result are not highly reliabile. This is particularly true for the youngest and oldest age groups, which tend to be the smallest in each panel, meaning we have the least confidence in each individual group-question estimate for these groups. We have attempted to limit this problem by averaging as many items as possible for each panel, but the number of questions in each panel is highly variable. |

>>>>

While we have parimarily focused on changes in the timing and structure of life course stages over the past 70 years, that time frame has also seen significant shifts in the broader social structure and cultural environment that might affect attitude stability independent of changes in life course structure. We briefly consider three broader changes here.

First, the number of people pursuing and completing higher education increased significantly over the window studied here [@schofer2005; @hout2012]. Existing work suggests that people with higher levels of education are more likely to express the same opinion over time in survey contexts [@alwin1991a; @alwin2007]. The specific mechanism that links educational attainment and attitude stability is unclear, with some perspectives suggesting educational attainment improves cognitive function and memory while other perspectives suggest that educational attainment makes people pay more attention to current events. It could also be that education cultivates in people an expectation that they hold opinions in the first place. Regardless of the specific mechanism, a population with higher levels of education, on average, might be more likely to hold stable opinions regardless of transformations in life course stages.

Second, technological changes have dramatically lowered barriers to accessing information, including information about social and political affairs that might facilitate stable opinion holding. Broadcast and cable television, followed by the internet and social media, have provided new channels for elites to communicate messages to the public and for people to acquire information that makes opinion-holding easier.

Third, the past 70 years have seen extensive elite polarization around political and social affairs, as well broader public partisan alignment [@fiorina2008; @baldassarri2008]. People now receive clearer signals from cultural elites, including politicians, the news media, and others, about which beliefs and identities "go together" in the population, resulting in what DellaPosta (2020) calls an "oil spill" of polarization [@dellaposta2020]. While clarity aroud political issue positions is most commonly studied, the same forces can also align other social beliefs and identities. This issue and identity alignment might make it easier for the public to identify what beliefs people like them "should" hold and hold them consistently [@zaller1992]. Geographic and social sorting into lifestyle "enclaves" also reinforce these processes, continually providing clearer signals about which opinions people should hold [@dellaposta2015].

@@

For reasons explained below, we identified questions that were asked in at least three different panels with at least one of those panels asking some respondents to answer the question at three or more separate time points. Because three of the GSS panels overlap considerably (2006-10, 2008-12, and 2010-14) and contain the same set of questions, we did not treat these as separate panels for the purposes of identifying three distinct time points. In other words, questions needed to appear in these panels and an ANES panel to be included in our analysis. We allowed for question wording to vary slightly across panels (e.g., feeling thermometers about "blacks" instead of "negros"). When the same or similar questions had slightly different response scales, we harmonized response options to the question structure with the fewest response options. This was most common when one panel asked whether people agreed or disagreed while another included options for "strong" agreement and disagreement. We broadly followed the ANES time series' lead in which questions to harmonize.

@@

Table A1 in Appendix A outlines the questions included in our analysis, including their full question wording and response scale.

@@

We are also interested in the effect of having undergone a set of life-course transitions on attitude stability to more directly test whether divergences in life course structure drove changes in attitude stability. To this end, we include a set of indicator variables capturing whether the respondent had undergone certain demographic transitions. These include 1) whether a respondent is currently enrolled in school; 2) whether a respondent has ever been married; and 3) whether a respondent has ever had a child. We also include an indicator for whether a respondent reported completing college to separately explore whether higher rates of college completion explain changes over time across age groups.

It was quite common for respondents to have missing data on demographic variables for a particular wave of any panel, even if they participated in the panel. This was most common when a question occurred in the post-election wave of the ANES, but demographic variables were captured in the pre-election wave. Similarly, some demographic items were only asked in one wave of a panel. When respondents were missing on a demographic item, we imputed the missing variable using first earlier responses and then, if there were no earlier responses, later responses.

Broadly speaking, questions tapping marital status, student status, and degree attainment tended to be asked in the same way with the same response options or could be easily harmonized. In contrast, generating a variable for whether a respondent had children was more challenging, as what information was being sought varied significantly across panels and even within panels. Specifically, questions occasionally tap how many children were currently living with the respondent and at other times tapped whether the respondent had any children or how many children the respondent had ever had. While these items are highly correlated for respondents with young children, these two approaches to the question produce significant differences in rates among parents whose children have left home.

To generate a measure of whether respondents had children, we ...

1990 pre: Number of children in house
1991: copied from 1990
1992: any children?
1992 post: copies from 1992pre
1993: copied from 1992 pre
1994: any children ever
96: Any children under 18 in household

@@

In this framework, the first-level equation models the absolute difference in a pair of responses to the same question given by the same respondent, similar to what was presented above. These equations are nested at the level of the survey item. In practice, the model presented in Eq \### is likely too complicated given our data limitations, and might not be necessary. As part of our analysis, we compare the fully elaborated model to more parsimonious models using model-selection criteria, specifically the Bayesian information criterion (BIC) and Akaike information criterion [@raftery1995]. For example, it could be the case that little predictive information is gained by allowing questions to have separate slopes for the relationship between age categories and duration over time.

@@

Once we select the most parsimonious model to capture attitude stability over time, we then include variables capturing demographic transitions to evaluate their relationship to attitude stability over time. To distinguish between the influence of life course structure and other factors that might be affecting attitude stability, such as broader social forces, we calculate the expected rate of attitude change in later panels holding constant the proportion of respondents in each group who made certain demographic transitions.

For each wave pair, we include measures of demographic status at the first observation. For example, if a respondent is unmarried at the first wave and gets married by the second, they are counted as "never married" for the purposes of our analysis. If they are observed a third time, they would be counted as "married" for that pair of waves.

### Weights

Finally, a key issue in drawing valid inferences about the U.S. population over time is to ensure that samples generalize to the same theoretical population -- the U.S. adult non-institutionalized population. However, none of the panels used in our analysis were simple random samples of the adult population. All employ different complex sampling strategies.

To account for this, we attempt to use weights that account for these sampling strategies as well as, when available, non-response.

@@

The intercept term in Model 1 suggests that, on average, survey respondents in the 18-25 age group are expected to vary by almost a fifth of the response scale on average (about 18 points) in the most recent years of the survey, controlling for duration between observations, on any particular question. This is a rather high level of variance, but it is consistent with previous studies that find that on any particular question survey respondents tend to make large wave-to-wave changes, or that survey questions about political attitudes have high levels of measurement error [@ansolabehere2009; @converse1965]. At the same time, random-effect variance around this main intercept term is quite large ($\sigma_{\beta_0} = 5.9220$). On several questions, respondents are expected to change their responses by about 40 percent of the scale between observations, while on others almost no wave-to-wave change is expected, meaning people tend to respond with the same answer over time with low levels of measurement error or random change.

Duration between observations is positively associated with wave-to-wave absolute change. For every additional year between responses, the expected absolute change for respondents increases 1.1 points. As suggested above by the model comparison, there is no evidence to suggest that respondents in different age groups vary systematically in this kind of change. Random effect variance around this main effect is relatively small (s.d. = 0.36), meaning each one-year duration only increases the amount changed by between .5 and 1.5 for most questions. Given the comparatively high level of wave-to-wave change independent of duration (18 points), our results broadly suggest that most wave-to-wave change is non-persisting, consistent with findings from other recent work [@kiley2020; @lersch2023].

The coefficients for age groups other than the reference category suggest that, on average, other age groups are more stable than people in the 18-25 age range in the most recent panels. Respondents in the 26-33 age group are about 1.1 points more stable on average, respondents in the 34-65 age group are about 2.2 points more stable on average, and respondents in the 65 and over age group are about 3.5 points more stable on average, than respondents in the 18-25 age group. This provides broad evidence for the "impressionable years" and "increasing persistence" hypotheses, as the youngest age groups are less stable than others, followed by the 26-33 age group.

Coefficients in Model 1 allow us to test several of the hypotheses outlined above. The intensification of early adulthood hypothesis (H3) generally suggests that the most recent cohorts should make the most change when they are in the youngest age range than cohorts that came before them. The effect of year of observation in decades for people in the 18-25 age group ($\beta = 0.14345$, $t = 0.754$) is substantively small and not statistically significantly different from 0. On average, recent cohorts in this age group make approximately the same amount of wave-to-wave change in recent years as earlier cohorts did, accounting for the kinds of questions they were asked and time between responses. However, question-level random effects vary considerably around this main effect, with a standard deviation of about 1.43. This suggests that the overall flat trend obscures quite large question-level differences, with some questions becoming more stable and others becoming less stable. We return to consider these question-specific trends later.

Next, the extended early adulthood framework (H1) suggests that we should see a closing of the gap between people in the 18-25 and 26-33 age groups over time. The interaction between year of observation and the 26-33 age category is small and not statistically significant ($\beta = -0.03560$, $p=-0.361$), suggesting that while people in this age group are more stable, on average, than then youngest respondents, more recent cohorts are not any more or less likely to make changes of opinion in this age range than earlier cohorts, and more recent cohorts are not any more or less similar to younger adults than earlier cohorts.

However, before drawing broader conclusions about the lack of importance of life course shifts, it is important to understand the full picture of change over time. Table XXX shows that, in contrast to people in the 18-25 and 26-33 age range whose rate of opinion change remains flat across cohorts, respondents in older age groups (34-64 and 65+) do show a notable time trend -- more recent cohorts are more stable opinion reports in these age ranges than earlier cohorts. To more clearly illustrate overall trends, Figure XXX plots the predicted time level of change for respondents in each age category over time.

@@

To evaluate the specific effect of life-course changes, we attempt to control for these transitions. We re-estimate Model \### above, this time incorporating a series of indicator variables for whether respondents were students, whether they had children, and whether they were married. We also include an indicator variable for whether the respondent completed college to capture the effect of ... .

@@

```{r}
new.data %>%
  filter(d == 2) %>%
  mutate(time = recode(time, "1"="Counterfactual", "t"="Observed")) %>%
  mutate(time = ifelse(dec_diff == -6.4, "Start", time)) %>%
  group_by(age_group, dec_diff, time) %>%
  summarise(yhat = mean(yhat)) %>%
  ungroup() %>%
  select(-dec_diff) %>%
  spread(time, yhat) %>%
  pivot_longer(Counterfactual:Observed) %>%
  mutate(Start.Time = -6.4, Finish.Time = 0) %>%
  ggplot(aes(x = Start.Time, xend = Finish.Time, y = Start, yend = value,
             linetype = name, color = age_group)) +
  geom_segment() + 
  geom_line(aes(color = age_group)) + 
  #geom_point(size = 3) +
  theme_bw() + 
  scale_shape_manual(values = c(21,22)) + 
  scale_fill_brewer(type = "qual", palette = 2,
                     guide = "none") + 
  scale_color_brewer(type = "qual", palette = 2,
                    guide = "none") + 
  labs(x = "Age Group", y = "Expected change for 2-year duration",
       shape = "Estimate",
       title = "Counterfactual expectation of change",
       subtitle = "Holding demographic variables constant at 1956 levels") + 
  facet_wrap(~age_group)

Assuming that rates of marriage, student status, and degree attainment remained constant at their 1956 level over time for each age group, age groups would be expected to display more similar rates of change in the most recent panels than they actually do. In particular, the youngest respondents would display lower rates of change over time and other age groups would display higher rates of change over time. In fact, consistent with the extended early adulthood framework, the youngest respondents would be slightly less consistent opinion holders in more recent years than they actually were.

This divergence between observed and counterfactual trajectories is principally driven by changes in college-going, rather than delays in marriage. The dramatic increase in college-going for all age groups produces more stable attitudes over time. However, because young people have completed college at lower rates than older respondents in the most recent panels (likely because many of them are still enrolled), they do not benefit as much from this shift (though being currently enrolled as a student also increases attitude stability). Young respondents' dramatically lower rates of marriage in the most recent panels counteracts the increased stability that comes from higher levels of educational attainment.

@@

Theoretical models that explain the heightened malleability of attitudes during early adulthood by referencing the unique social conditions of that life phase suggest that significant changes in the timing of life course events should produce heightened rates of attitude change during early adulthood (18-25) or should extend rates of attitude updating later into life (ages 26-33). Given that Americans, on average, pushed back marriage, childbirth, and entering the workforce over the course of the second half of the 20th Century and the early 21st Century, we posited that these shifts should, through various pathways, increase over-time variance in survey responses among the youngest members of the population. We tested that hypothesis by looking at the stability of political and social attitudes among different cohorts as they moved through the same age groups.

The results presented above suggest a more complicated picture than anticipated. Consistent with expectations, the youngest adults look similar to older adults in the earliest panels in terms of both demographics and attitude stability. While members of the youngest age categories (18-25 and 26-33) diverged over time from older members of the population in the rate at which they changed their opinions, showing more change than older respondents in the most recent panels, this shift was principally driven by an increase in stability among people in middle age and over 65, rather than increased opinion change among the youngest adults. We suggested that this aggregate divergence was driven by countervailing trends. On one hand, delays in life course transitions push the youngest members of the population to make more attitude change over time. Second, broader social forces worked to stabilize opinions for all members of the population, leading to divergence between the youngest adults and the rest of the population.

We tested this proposition using data on life-course transitions and measures of educational attainment. We found that, consistent with our revised perspective of countervailing forces, age groups' rates of attitude change over time would have been more similar if these social changes did not happen. Specifically, increased rates of educational attainment account for much of the stabilizing shifts among older Americans, while delayed rates of marriage and childbearing decreased attitude stability among the youngest members of the population.

Our results suggest that broad social conditions play a substantial role in shaping the rate at which people change their attitudes. Since the 1950s, Americans have become meaningfully more stable opinion holders, in part because they have attained higher levels of education. Our approach likely under-estimates the importance of this shift, as we focus principally on rising rates of college attainment. However, in the earliest panels, a substantial proportion (> 70 percent) of the oldest respondents and more than 50 percent of middle aged respondents lacked a high school degree.

Changes in the timing of life-course events were less important than changes in education for explaining, but they do play a role. Our findings suggest that, in the absence of these delays, young people would make attitude changes at a comparable rate to that of older people.

At the same time, it is important not to overstate the importance of these broader social transitions. Despite dramatic shifts in educational attainment, access to information, and political organization, people make changes in many social and political attitudes at the same rates they did 70 years ago.

@@

There are theoretically relevant trade-offs from focusing only on the same questions over time. By focusing only on the same questions over time, we control for question content and structure and ensure that the trend over time is due to something other than changes in survey administration. Because our panels span more than five decades that saw dramatic improvements in survey question design, questions included in more recent surveys might simply be of higher quality, with less wave-to-wave change, than items included in older surveys.

We face several limitations in trying to make broader claims. First, many of our age-group estimates of stability and reliability are based on relatively small samples and as a result are not highly reliabile. This is particularly true for the youngest and oldest age groups, which tend to be the smallest in each panel, meaning we have the least confidence in each individual group-question estimate for these groups. We have attempted to limit this problem by averaging as many items as possible for each panel, but the number of questions in each panel is highly variable.
